\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: Revision of Section 4.3

In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following \citet{saffman_1986} work. In this work, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem formulation and solution.

Here, 2D simulations are conducted in 5$\times$5 domain, Fig.~\ref{fig:homoheleshaw}(a) fully saturated with a fluid. Wetting phase fluid is injected from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$. A zero-flux condition was applied to all boundaries, except the top right-hand corner (named as sink).
XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
 of the problem. formation and stability of viscous flow instaseminal work of \citet{saffman_1986}
Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}-%,\ref{fig:1b_homoheleshaw_3} 
\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations. In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
. The sink (pressure set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
was imposed to all borders of the domain except at the top righ hand side corner. The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.

>>>>

In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following \citet{saffman_1986} work. In this work, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem mathematical formulation and solutions.

Here, 2D simulations were conducted in a 5$\times$5 unit-length domain (Fig.~\ref{fig:homoheleshaw}a) fully saturated with a fluid. Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$. Newmann boundary condition (\ie, no flux) was imposed to all borders of the domain except at the top right-hand corner (named as sink). Viscosity ratios for this set of simulations are 3 and 10.
